Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-07-14 tensor/draft/draft-tensor-op.tex
[draft, mcmc] clarify jacobian issue

In total, there are 19 parameters $\alpha^i_j$ to describe $B\to K^*$ form
factors and most of them are strongly correlated. But it is well known that
strong correlation leads to poor sampling as it can cause the random-walk Markov
chains to spend significant time in regions of low probability and thus produce
spurious peaks. To mitigate this issue, we perform a fit to form-factor
constraints without any experimental data and use the resulting covariance
matrix to transform parameters such that the new parameters are uncorrelated. \todo{Why no Jacobian involved?}

>>>>

In total, there are 19 parameters $\alpha^i_j$ to describe $B\to K^*$ form
factors and most of them are strongly correlated. But it is well known that
strong correlation leads to poor sampling as it can cause the random-walk Markov
chains to spend an excessive amount of time in regions of low probability and
thus produce spurious peaks. To mitigate this issue, we perform a fit to
form-factor constraints without any experimental data and use the resulting
covariance matrix to transform parameters such that the new parameters are
uncorrelated.
